% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,oneside]{article}
%\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVTitle}{Minshu Zhan's CV}
\newcommand{\CVNote}{CV compiled on {\today}}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={Minshu Zhan},
pdfsubject={},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Minshu Zhan}

\begin{subtitle}
45 Nixon Street, Boston, MA 02124
\par
\href{mailto:minshuzhan@gmail.edu}
{minshuzhan@gmail.edu}
\,\BulletSymbol\,
+1\,(202)\,999-5564
%\,\BulletSymbol\,
\end{subtitle}

\begin{body}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Overview}
{Overview}
{PDF:Overview}
Two years backend experience in object-oriented programming and data modeling. Three years of code-heavy research experiences. 
Proficient in Java, Python, PostgreSql. Familiar with shell, redux pattern, javascript, HTML. Enjoy working tightly with problem-driven, fast-paced interdescriplinary teams. Care about delivering usable products.

%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work Experience}
{Work}
{PDF:Work}

\textbf{BevSpot}
\hfill Boston, MA
\par
Software Engineer
\hfill
\DatestampYM{2016}{04} --
present
\BulletItem Designed backend of accounting functionality for inventory transfer between and implemented using java and postgresql; handled data migration
\BulletItem maintanence of system featuring of multiple codebases and databases and frontend frameworks, transitioning from Django, naive javascript,document database to Java - postgres - redux
\BulletItem built front-end of various pages in redux patterns with TypeScript
\BulletItem implement digest email content and subscription end-to-end
%\BulletItem work tightly with product, design, and customer support teams on improving user experience

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Academic Experience}
{Academic}
{PDF:Academic}

\textbf{LabROSA}, Columbia University
\hfill New York, NY
\par Graduate Researcher
\hfill
\DatestampYM{2015}{01} --
\DatestampYM{2015}{05}
\BulletItem Conceptualized a probabilistic model for music recommendation which uses audio content and peer usage
information to infer the positions of users and songs in a common latent taste space.
\BulletItem Extracted high quality audio content features for about a million songs using clustering-based vector quantization
and a multilayer convolutional neural network.
\BulletItem Overcame the “cold start” problem met by traditional content-blind recommendation approaches and achieved better performance than rival content-aware methods.

\textbf{Anyscale Learning for All Group}, MIT CSAIL
\hfill Cambridge, MA
\par Graduate Researcher
\hfill
\DatestampYM{2013}{09} --
\DatestampYM{2014}{05}
\BulletItem
Augmented the program auto-tuning system \emph{OpenTuner} with a set of discrete-domain stochastic search algorithms, i.e. genetic algorithm, particle swarm optimization, and differential evolution. 
\BulletItem
Evaluated the system in multiple application domains and demonstrated that programs tuned by the extended
system runs up to 4x faster than those tuned by the original system.

\textbf{Personal Robots Group}, MIT Media Lab
\hfill Cambridge, MA
\par Graduate Researcher
\hfill
\DatestampYM{2013}{02} --
\DatestampYM{2013}{08}
\BulletItem Created a graphical interactive query-by-example audio retrieval software that allows the user to control the
direction of search and improve the results through feedback.
\BulletItem Delivered video demonstration and conference-style paper.
 

\textbf{Speech Communication Group},
MIT RLE
\hfill Cambridge, MA
\par
Undergraduate Research Student
\hfill
\DatestampYM{2012}{01} --
\DatestampYM{2013}{06}
\begin{detail}
\BulletItem
Implemented a tree-based classifier that predicts changes of speech acoustic landmarks based on their prosodic
contexts; engineered and selected features for the classification task.
\end{detail}

%\SmallEntryGap
%
%\textbf{Future Urban Mobility Group}, Singapore-MIT Alliance for Res. \& Tech.
%\hfill Singapore
%\par
%Undergraduate Research Student
%\hfill
%\DatestampYM{2011}{06} --
%\DatestampYM{2011}{08}
%\begin{detail}
%\BulletItem
%Project:
%Integrated Transportation Simulation Platform: SimMobility
%\BulletItem
%Contribution: Developed a large-scale GIS map interaction tool.
%\end{detail}


%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\textbf{Columbia University}
\hfill New York, NY
\par
Ph.D in Signal Processing (discontinued)
\hfill
\DatestampYM{2014}{09} -- \DatestampYM{2015}{12}
\begin{detail}
\BulletItem
Research areas:
music information retrieval, machine learning
\end{detail}

\SmallEntryGap

\textbf{Massachusetts Institute of Technology}
\hfill Cambridge, MA
\par
M.Eng. in
Computer Science
\hfill
\DatestampYM{2013}{09} --
\DatestampYM{2014}{06}
\begin{detail}
\BulletItem
Concentration: Artificial Intelligence
\BulletItem
Cumulative GPA: 4.5 / 5.0
\end{detail}

B.S. in Computer Science
\hfill
\DatestampYM{2009}{09} --
\DatestampYM{2013}{06}
\begin{detail}
\BulletItem
Cumulative GPA: 4.3 / 5.0
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section
%{Work Experience}
%{Other Work Experience}
%{PDF:OtherWorkExperience}
%
%\textbf{Introduction to EECS},
%MIT \hfill Cambridge, MA
%\par
%Lab Assistant
%\hfill
%\DatestampYM{2013}{02} --
%\DatestampYM{2013}{05}
%% detail?
%
%\EntryGap
%
%\textbf{Digital Communication System},
%MIT \hfill Cambridge, MA
%\par
%Teaching Assistant
%\hfill
%\DatestampYM{2012}{09} --
%\DatestampYM{2012}{12}
%% detail?


%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\section
{Publication}
{Publication}
{PDF:Publications}

\href{http://ismir2015.uma.es/articles/290_Paper.pdf}
{D. Liang, \underline{M. Zhan}, \& Ellis, D. (2015).
Content-Aware Collaborative Music Recommendation Using Pre-trained Neural Networks. Proceedings of \textit{International Society for Music Information Retrieval},
Málaga, Spain, 
\DatestampYM{2015}{10}.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC HONORS & AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Awards \& \newline Scholarships}
{Academic Honors \& Awards}
{PDF:AcademicHonorsAwards}

\textbf{Integrative Graduate Education and Research Traineeship}, Columbia University
\hfill
\DatestampYM{2014}{09} 

\SmallEntryGap

\textbf{EECS Undergraduate Research and Innovations Scholar}, MIT
\hfill
\DatestampYM{2012}{09}

\SmallEntryGap

\textbf{Singapore-MIT Undergraduate Research Fellowship}, MIT
\hfill
\DatestampYM{2011}{06}


%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%
%
%\section
%{Campus Activities}
%{Campus Activities}
%{PDF:CampusActivities}
%
%\textbf{MIT Syncopasian A Cappella Group}
%\hfill Cambridge, MA
%\par
%President
%\hfill
%\DatestampYM{2010}{02} --
%\DatestampYM{2012}{06}
%\begin{detail}
%Conducted regular group meetings and coordinated performances including bi-annual concerts. 
%\end{detail}
%\textbf{Next Act}
%\hfill Cambridge, MA
%\par
%Vocal Director
%\hfill
%\DatestampYM{2012}{01} --
%\DatestampYM{2012}{04}
%\begin{detail}
%Lead weekly vocal rehearsals for a 20-performer ensemble.
%\end{detail}



%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

%\section
%{Interests}
%{Interests}
%{PDF:Interests}
%
%Digital photography,
%typography,
%swimming.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

%\section
%{References}
%{References}
%{PDF:References}

%\textbf{Professor Jonathan Public}
%\par
%Professor of Geology and Mechanical Engineering
%\begin{detail}
%First American University
%\par
%Department of Geophysical Engineering
%\par
%1000 First Avenue, Springfield, Massachusetts 22222, USA
%\par
%\href{mailto:jonathanpublic@example.com}
%{jonathanpublic@example.com}
%\,\BulletSymbol\,
%+1\,(555)\,222-2222
%\end{detail}
%
%\EntryGap
%\textbf{Dr Alice Bob Carol}
%\par
%Director, Research \& Development
%\begin{detail}
%Alpha Engineering Firm
%\par
%20 North Street, Oakland, Ohio 33333, USA
%\par
%\href{mailto:alicebobcarol@example.com}
%{alicebobcarol@example.com}
%\,\BulletSymbol\,
%+1\,(555)\,333-3333
%\end{detail}



\end{body}

\end{document}
